### 2019-04-01 2-Chapters/6-Chapter/chapter6.tex
WOrking on the whole document but not yet Chapter5

Finally, we give extensive numerical experiments to compare our approach, in its two variants, against the current state-of-the-art policies, on different piece-wise stationary bandit problems, of increasing difficulty.
%
We also include additional details about our policy \GLRklUCB, including a sensibility analysis of its two parameters, a numerical evaluation of its time and memory costs, as well as details on an easy but efficient way to speed up the B-GLRT test while not loosing too much in terms of regrets.

>>>>

Finally, we give extensive numerical experiments to compare our approach, in its two variants, against the current state-of-the-art policies, on different piece-wise stationary bandit problems, of increasing difficulty.
%
We also include additional details about our policy \GLRklUCB, including a sensitivity analysis of its two parameters, a numerical evaluation of its time and memory costs, as well as details on an easy but efficient way to speed up the B-GLRT test while not loosing too much in terms of regrets.

### 2019-04-01 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Minitoc shows only Section, it's better.
Add Figures for Appendix of Chapter4
WOrking on the whole document but not yet Chapter5

        \log\ell(X_1, \ldots, X_n ; \mu_0,\mu_1,\tau)

@@

\begin{figure}[h!]
    \centering
    \begin{framed}
    % \begin{small}
    % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
    % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
    % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
    \begin{algorithm}[H]
        % XXX Options
        % \LinesNumbered  % XXX Option to number the line
        % \RestyleAlgo{boxed}
        % XXX Input, data and output
        \KwIn{\emph{Problem parameters}: $T\in\N^*$, $K\in\N^*$\;}
        \KwIn{\emph{Algorithm parameters}: exploration probability $\alpha \in (0, 1)$, confidence level $\delta>0$\;}
        \KwIn{\emph{Option}: \textbf{Local} or \textbf{Global} restart\;}
        % \KwData{Data}
        % \KwResult{Result}
        % XXX Algorithm
        \textbf{Initialization: } $\forall i \in \{1,\dots,K\}$, $\tau_i \leftarrow 0$ and $n_i \leftarrow 0$ \\
        \For{$t=1,2,\ldots, T$}{
            \uIf{
                $\alpha>0$ and $t \mod \left\lfloor \frac{K}{\alpha}\right\rfloor \in \{1,\dots,K\}$
            }{
                $A_t \leftarrow t \mod \left\lfloor \frac{K}{\alpha}\right\rfloor$
                \tcp*[f]{forced exploration} \\
            }
            \Else{
                $A_t \leftarrow \arg\max\limits_{i\in \{1,\dots,K\}} \mbox{UCB}_i(t)$ as defined in \eqref{def:6:UCB}
            }
            \mbox{Play arm } $A_t$ \mbox{and receive the reward } $X_{A_t,t}$ : $n_{A_t} \leftarrow n_{A_t} + 1; Z_{A_t, n_{A_t}} \leftarrow X_{A_t,t}$ \\
            \uIf(\tcp*[f]{Change point is detected}){
                $\GLR_\delta(Z_{A_t,1}, \ldots, Z_{A_t, n_{A_t}})$ = True
            }
            {
                \uIf{Global restart}{
                    $\forall i\in \{1,\dots,K\}, \tau_i \leftarrow t$ and $n_i \leftarrow 0 $.
                    \tcp*[f]{global restart}
                    }
                \Else{
                    $\tau_{A_t} \leftarrow t$ and $n_{A_t} \leftarrow 0$
                    \tcp*[f]{local restart}
                }
            }
        }
        \caption{\GLRklUCB, with \textbf{Local} or \textbf{Global} restarts}
        \label{algo:6:GLRklUCB}
    \end{algorithm}
    % \end{small}
    \end{framed}
\end{figure}

@@

The \GLRklUCB{} algorithm can be viewed as a \klUCB{} algorithm allowing for some \emph{restarts} on the different arms. A restart happens when the B-GLRT change-point detector detects a change on the arm that has been played (line $9$).
%
To be fully specific, $\GLR_\delta(Z_1,\dots,Z_n) = \mathrm{True}$ if and only if
\begin{equation}\label{eq:whenDoesGLRklUCBrestart}
    \sup_{1 < s < n} \left[s \times \kl \left(\frac{1}{s}\sum_{i=1}^s Z_i , \frac{1}{n}\sum_{i=1}^n Z_i\right) + (n-s) \times \kl \left(\frac{1}{n-s}\sum_{i=s+1}^t Z_i , \frac{1}{n}\sum_{i=1}^n Z_i\right)\right] \geq \beta(n,\delta),
\end{equation}
%
with $\beta(n,\delta)$ defined in \eqref{def:6:beta}, or $\beta(n,\delta) = \ln(3n^{3/2}/\delta)$, as recommended in practice, see Section~\ref{sub:6:PracticalConsiderations}. We define the (\klUCB{} like) index used by our algorithm, by denoting
$\tau_i(t)$ the last restart that happened for arm $i$ before time $t$,
$n_i(t) = \sum_{s=\tau_i(t)+1}^{t} \indic(A_s=i)$
the number of selections of arm $i$, and
$\widehat{\mu}_i(t) = \frac{1}{n_i(t)} \sum_{s=\tau_i(t)+1}^{t}X_{i,s} \indic(A_s=i)$
their empirical mean (if $n_i(t)\neq0$).
%
With the exploration function $f(t) = \ln(t) + 3 \ln(\ln(t))$ if $t>1$ and $f(t)=0$ otherwise,
the index is defined using the binary relative entropy as
%
\begin{equation}\label{def:6:UCB}
    \UCB_i(t) := \max \Bigl\{ q\in[0,1] : n_i(t) \times \kl\left(\widehat{\mu}_i(t),q\right) \leq f(t - \tau_i(t)) \Bigr\}.
\end{equation}

@@

%-----------------------------------------------------------------------------
\subsection{Proof of the regret upper-bounds}
\label{sec:6:proofRegret}

\TODOL{Write intro}

@@

\paragraph{Upper bound on term $\bm{(A)}$.}

@@

\paragraph{Upper bound on term $\bm{(B)}$.}
%
We let $\tilde{\mu}_{i,s}^{(k)}$ denote the empirical mean of the first $s$ observations of arm $i$ made after time $t=\hat{\tau}^{(k)}+1$. Rewriting the sum in $t$ as the sum of consecutive intervals $[\tau^{(k)}+1, \tau^{(k+1)}]$,
%
\begin{align*}
    (B) & \leq \bE\Big[\indic(\cE_T)\sum_{k=1}^{\Upsilon_T} \sum_{t=\tau^{(k)}}^{\tau^{(k+1)}}\left(\mu_{k^*}^{(k)} - \mu_{I_t}^{(k)}\right)\indic\left(\UCB_{I_t}(t) \geq \mu_{k^*}^{(k)}\right)\Big] \\
     & \leq \sum_{k=1}^{\Upsilon_T}\bE\Big[\indic(\cE_T)\hat{\tau}^{(k)} + \indic(\cE_T) \sum_{t=\widehat{\tau}^{(k)}+1}^{\tau^{(k+1)}}\left(\mu_{k^*}^{(k)} - \mu_{I_t}^{(k)}\right)\indic\left(\UCB_{I_t}(t) \geq \mu_{k^*}^{(k)}\right)\Big] \\
    & \leq \sum_{k=1}^{\Upsilon_T}d_i^{(k)}+ \sum_{i=1}^K \bE\Big[\indic(\cE_T) \sum_{t=\widehat{\tau}^{(k)}+1}^{\tau^{(k+1)}}\left(\mu_{k^*}^{(k)} - \mu_{i}^{(k)}\right)\indic\left(I_t=i,\UCB_{i}(t) \geq \mu_{k^*}^{(k)}\right)\Big] \\
    & \leq \sum_{k=1}^{\Upsilon_T}d_i^{(k)}+ \sum_{i=1}^K \sum_{k=1}^{\Upsilon_T}\left(\mu_{k^*}^{(k)} - \mu_{i}^{(k)}\right)\times \\
    &\hspace{1cm}\bE\Big[\indic(\cE_T) \sum_{t=\hat{\tau}^{(k)}+1}^{\tau^{(k+1)}}\sum_{s=1}^{t-\widehat{\tau}^{(k)}}\indic\left(I_t = i,n_i(t) = s\right) \indic\left(s \, \kl(\tilde{\mu}_{i,s}^{(k)}, \mu_{k^*}^{(k)}) \leq f(\tau^{(k+1)} - \widehat{\tau}^{(k)})\right)\Big]
\end{align*}
\begin{align*}
    & \leq \sum_{k=1}^{\Upsilon_T}d_i^{(k)}+ \sum_{i=1}^K \sum_{k=1}^{\Upsilon_T}\left(\mu_{k^*}^{(k)} - \mu_{i}^{(k)}\right)\bE\Big[\indic(\cE_T) \sum_{s=1}^{n_i(\tau^{(k+1)})}\indic\left(s \, \kl(\tilde{\mu}_{i,s}^{(k)}, \mu_{k^*}^{(k)}) \leq f(\tau^{(k+1)} - \tau^{(k)})\right)\Big]  \\
    & \leq \sum_{k=1}^{\Upsilon_T}d_i^{(k)}+ \sum_{i=1}^K \sum_{k=1}^{\Upsilon_T}\left(\mu_{k^*}^{(k)} - \mu_{i}^{(k)}\right)\bE\Big[\indic(\cC^{(k)}) \sum_{s=1}^{n_i(\tau^{(k+1)})}\indic\left(s \, \kl(\tilde{\mu}_{i,s}^{(k)}, \mu_{k^*}^{(k)}) \leq f(\tau^{(k+1)} - \tau^{(k)})\right)\Big].
\end{align*}

@@

>>>>

        & \log\ell(X_1, \ldots, X_n ; \mu_0,\mu_1,\tau) \\

@@

\begin{figure}[h!]
    \centering
    \begin{framed}
    % \begin{small}
    % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
    % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
    % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
    \begin{algorithm}[H]
        % XXX Options
        % \LinesNumbered  % XXX Option to number the line
        % \RestyleAlgo{boxed}
        % XXX Input, data and output
        \KwIn{\emph{Problem parameters}: $T\in\N^*$, $K\in\N^*$\;}
        \KwIn{\emph{Parameters}: exploration probability $\alpha \in (0, 1)$, confidence level $\delta>0$\;}
        \KwIn{\emph{Option}: \textbf{Local} or \textbf{Global} restart\;}
        % \KwData{Data}
        % \KwResult{Result}
        % XXX Algorithm
        \textbf{Initialization: } $\forall i \in \{1,\dots,K\}$, $\tau_i \leftarrow 0$ and $n_i \leftarrow 0$ \\
        \For{$t=1,2,\ldots, T$}{
            \uIf{
                $\alpha>0$ and $t \mod \left\lfloor \frac{K}{\alpha}\right\rfloor \in \{1,\dots,K\}$
            }{
                $A_t \leftarrow t \mod \left\lfloor \frac{K}{\alpha}\right\rfloor$
                \tcp*[f]{forced exploration} \\
            }
            \Else{
                $A_t \leftarrow \arg\max\limits_{i\in \{1,\dots,K\}} \mbox{UCB}_i(t)$ as defined in \eqref{def:6:UCB}
            }
            \mbox{Play arm } $A_t$ \mbox{and receive the reward } $X_{A_t,t}$ : $n_{A_t} \leftarrow n_{A_t} + 1; Z_{A_t, n_{A_t}} \leftarrow X_{A_t,t}$ \\
            \uIf(\tcp*[f]{Change point is detected}){
                $\GLR_\delta(Z_{A_t,1}, \ldots, Z_{A_t, n_{A_t}})$ = True
            }
            {
                \uIf{Global restart}{
                    $\forall i\in \{1,\dots,K\}, \tau_i \leftarrow t$ and $n_i \leftarrow 0 $.
                    \tcp*[f]{global restart}
                    }
                \Else{
                    $\tau_{A_t} \leftarrow t$ and $n_{A_t} \leftarrow 0$
                    \tcp*[f]{local restart}
                }
            }
        }
        \caption{\GLRklUCB, with \textbf{Local} or \textbf{Global} restarts}
        \label{algo:6:GLRklUCB}
    \end{algorithm}
    % \end{small}
    \end{framed}
\end{figure}

@@

The \GLRklUCB{} algorithm can be viewed as a \klUCB{} algorithm allowing for some \emph{restarts} on the different arms. A restart happens when the B-GLRT change-point detector detects a change on the arm that has been played (line $9$).
%
To be fully specific, $\GLR_\delta(Z_1,\dots,Z_n) = \mathrm{True}$ if and only if
\begin{equation}\label{eq:whenDoesGLRklUCBrestart}
    \sup_{1 < s < n} \left[s \times \kl \left(\frac{1}{s}\sum_{i=1}^s Z_i , \frac{1}{n}\sum_{i=1}^n Z_i\right) + (n-s) \times \kl \left(\frac{1}{n-s}\sum_{i=s+1}^t Z_i , \frac{1}{n}\sum_{i=1}^n Z_i\right)\right] \geq \beta(n,\delta),
\end{equation}
%
with $\beta(n,\delta)$ defined in \eqref{def:6:beta}, or $\beta(n,\delta) = \ln(3n^{3/2}/\delta)$, as recommended in practice, see Section~\ref{sub:6:PracticalConsiderations}. We define the (\klUCB{} like) index used by our algorithm, by denoting
$\tau_i(t)$ the last restart that happened for arm $i$ before time $t$,
$n_i(t) = \sum_{s=\tau_i(t)+1}^{t} \indic(A_s=i)$
the number of selections of arm $i$, and
$\widehat{\mu}_i(t) = \frac{1}{n_i(t)} \sum_{s=\tau_i(t)+1}^{t}X_{i,s} \indic(A_s=i)$
their empirical mean (if $n_i(t)\neq0$).
%
With the exploration function $f(t) = \ln(t) + 3 \ln(\ln(t))$ if $t>1$ and $f(t)=0$ otherwise,
the index is defined using the binary relative entropy $\kl$ as
%
\begin{equation}\label{def:6:UCB}
    \UCB_i(t) := \max \Bigl\{ q\in[0,1] : n_i(t) \times \kl\left(\widehat{\mu}_i(t),q\right) \leq f(t - \tau_i(t)) \Bigr\}.
\end{equation}

@@

%-----------------------------------------------------------------------------
\section{Proof of the regret upper-bounds}
\label{sec:6:proofRegret}

@@

\paragraph{Upper bound on term $(A)$.}

@@

\paragraph{Upper bound on term $(B)$.}
%
We let $\tilde{\mu}_{i,s}^{(k)}$ denote the empirical mean of the first $s$ observations of arm $i$ made after time $t=\hat{\tau}^{(k)}+1$. Rewriting the sum in $t$ as the sum of consecutive intervals $[\tau^{(k)}+1, \tau^{(k+1)}]$,
%
\begin{align*}
    (B) & \leq \bE\Big[\indic(\cE_T)\sum_{k=1}^{\Upsilon_T} \sum_{t=\tau^{(k)}}^{\tau^{(k+1)}}\left(\mu_{k^*}^{(k)} - \mu_{I_t}^{(k)}\right)\indic\left(\UCB_{I_t}(t) \geq \mu_{k^*}^{(k)}\right)\Big] \\
     & \leq \sum_{k=1}^{\Upsilon_T}\bE\Big[\indic(\cE_T)\hat{\tau}^{(k)} + \indic(\cE_T) \sum_{t=\widehat{\tau}^{(k)}+1}^{\tau^{(k+1)}}\left(\mu_{k^*}^{(k)} - \mu_{I_t}^{(k)}\right)\indic\left(\UCB_{I_t}(t) \geq \mu_{k^*}^{(k)}\right)\Big] \\
    & \leq \sum_{k=1}^{\Upsilon_T}d_i^{(k)}+ \sum_{i=1}^K \bE\Big[\indic(\cE_T) \sum_{t=\widehat{\tau}^{(k)}+1}^{\tau^{(k+1)}}\left(\mu_{k^*}^{(k)} - \mu_{i}^{(k)}\right)\indic\left(I_t=i,\UCB_{i}(t) \geq \mu_{k^*}^{(k)}\right)\Big] \\
    & \leq \sum_{k=1}^{\Upsilon_T}d_i^{(k)}+ \sum_{i=1}^K \sum_{k=1}^{\Upsilon_T}\left(\mu_{k^*}^{(k)} - \mu_{i}^{(k)}\right)\times \\
    &\hspace{1cm}\bE\Big[\indic(\cE_T) \sum_{t=\hat{\tau}^{(k)}+1}^{\tau^{(k+1)}}\sum_{s=1}^{t-\widehat{\tau}^{(k)}}\indic\left(I_t = i,n_i(t) = s\right) \indic\left(s \, \kl(\tilde{\mu}_{i,s}^{(k)}, \mu_{k^*}^{(k)}) \leq f(\tau^{(k+1)} - \widehat{\tau}^{(k)})\right)\Big]
\end{align*}
\begin{align*}
    & \leq \sum_{k=1}^{\Upsilon_T}d_i^{(k)}+ \sum_{i=1}^K \sum_{k=1}^{\Upsilon_T}\left(\mu_{k^*}^{(k)} - \mu_{i}^{(k)}\right)\bE\Big[\indic(\cE_T) \sum_{s=1}^{n_i(\tau^{(k+1)})}\indic\left(s \, \kl(\tilde{\mu}_{i,s}^{(k)}, \mu_{k^*}^{(k)}) \leq f(\tau^{(k+1)} - \tau^{(k)})\right)\Big]  \\
    & \leq \sum_{k=1}^{\Upsilon_T}d_i^{(k)}+ \sum_{i=1}^K \sum_{k=1}^{\Upsilon_T}\left(\mu_{k^*}^{(k)} - \mu_{i}^{(k)}\right)\bE\Big[\indic(\cC^{(k)}) \sum_{s=1}^{n_i(\tau^{(k+1)})}\indic\left(s \, \kl(\tilde{\mu}_{i,s}^{(k)}, \mu_{k^*}^{(k)}) \leq f(\tau^{(k+1)} - \tau^{(k)})\right)\Big].
\end{align*}

@@

\TODOL{I could add the following algorithms, just to illustrate more:

- OracleRestart with UCB
- M- and CUSUM- with UCB (as defined in the papers)
- Exp3.S
}

### 2019-04-01 4-Listofpublications/Listofpublications.tex
Show change.
WOrking on the whole document but not yet Chapter5

\section*{International Conferences}
\renewcommand{\labelenumi}{[IC-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://perso.crans.org/besson/articles/BBM__IEEE_WCNC_2019.pdf}{GNU
  Radio Implementation of MALIN: « Multi-Armed bandits Learning for
  Internet-of-things Networks »}, by \textbf{L. Besson},
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2019.ieee-wcnc.org/}{IEEE WCNC},
  Marrakech, Maroc, April 2019, \href{https://hal.inria.fr/hal-02006825}{HAL-02006825}.
\item
  \href{https://perso.crans.org/besson/articles/BBM__Demo_ICT_2018.pdf}{MALIN:
  « Multi-Arm bandit Learning for Iot Networks » with GRC: A TestBed
  Implementation and Demonstration that Learning Helps}, by \textbf{L.
  Besson}, \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}. Demonstration
  presented at ICT (\emph{International Conference on Communication}),
  Saint-Malo, France, June 2018. Cf. \texttt{YouTu.be/HospLNQhcMk}, \href{https://hal.inria.fr/hal-02013866}{HAL-02013866}
\item
  \href{https://hal.inria.fr/hal-01629733/document}{Multi-Player Bandits
  Revisited}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}.
  \href{http://www.cs.cornell.edu/conferences/alt2018/accepted.html}{ALT}
  (\emph{Algorithmic Learning Theory}), Lanzarote, Spain, April 2018,
  \href{https://hal.inria.fr/hal-01629733}{HAL-01629733}.
\item
  \href{https://hal.inria.fr/hal-01705292/document}{Aggregation of
  Multi-Armed Bandits learning algorithms for Opportunistic Spectrum
  Access}, by \textbf{L. Besson},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2018.ieee-wcnc.org/}{IEEE WCNC}, Barcelone, Spain,
  avril 2018, \href{https://hal.inria.fr/hal-01705292}{HAL-01705292}.
\item
  \href{https://hal.inria.fr/hal-01575419/document}{Multi-Armed Bandit
  Learning in IoT Networks and non-stationary settings}, par
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L.
  Besson}, \href{https://moychris.wordpress.com/}{C. Moy},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& J. Palicot. \href{http://crowncom.org/2017/}{CrownCom}
  (\emph{Conference on Cognitive Radio Oriented Wireless Networks}),
  Lisbonne, Portugal, septembre 2017,
  \href{https://hal.inria.fr/hal-01575419}{HAL-01575419}, \textbf{prix
  du meilleur article}.
\end{etaremune}

@@

\section*{Other National Communications}
\renewcommand{\labelenumi}{[ONC-\arabic{enumi}]}
\begin{etaremune}
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{Journ\'{e}e Des Doctorants de l'IETR}, Rennes, France, Jul 2017, \href{https://hal.inria.fr/hal-02013847}{HAL-02013847}
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{SCEE Seminar}, Rennes, France, Mar 2017
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{SCEE Seminar}, Rennes, France, Mar 2017
	\item	R. Bonnefoi, \textbf{L. Besson}, ``Multi-Armed Bandit Learning in IoT Networks'', in \emph{Journ\'{e}e Des Doctorants de l'IETR}, Rennes, France, Jun 2016, \href{https://hal.inria.fr/hal-02013839}{HAL-02013839}
\end{etaremune}

\section*{Other Publications}
\renewcommand{\labelenumi}{[OP-\arabic{enumi}]}
\begin{etaremune}
\item
	\href{https://perso.crans.org/besson/articles/BMBBM__IEEE_WCNC__2019.pdf}{Upper-Confidence
	Bound for Channel Selection in LPWA Networks with Retransmissions},
	par \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L. Besson}, J.
	Manco-Vasquez,
	\href{https://moychris.wordpress.com/}{C. Moy}. Septembre 2018.
\item
	\href{https://hal.inria.fr/hal-01840022/document}{SMPyBandits: an
	Open-Source Research Framework for Single and Multi-Players Multi-Arms
	Bandits (MAB) Algorithms in Python}, by \textbf{L. Besson},
	développement depuis octobre 2016 et encore actif,
	\href{https://hal.inria.fr/hal-01840022}{HAL-01840022}. Code sur
	\href{https://GitHub.com/SMPyBandits/SMPyBandits}{GitHub.com/SMPyBandits}
	(environ 40000 lignes), documentation sur
	\href{https://SMPyBandits.rtfd.io}{SMPyBandits.rtfd.io}.
\item
	\href{https://hal.inria.fr/hal-01736357/document}{What Doubling-Trick
	Can and Can't Do for Multi-Armed Bandits}, by \textbf{L. Besson} \&
	\href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
	Kaufmann}, septembre 2018,
	\href{https://hal.inria.fr/hal-01736357}{HAL-01736357}.
\item
	\href{https://hal.inria.fr/hal-01847480/document}{A Note on the Ei
	Function and a Useful Sum-Inequality}, by \textbf{L. Besson}, février
	2018 \href{https://hal.inria.fr/hal-01847480}{HAL-01847480}.
\end{etaremune}

>>>>

\section*{International Conferences}
\renewcommand{\labelenumi}{[IC-\arabic{enumi}]}
\begin{etaremune}
\item
	\href{https://perso.crans.org/besson/articles/BMBBM__IEEE_WCNC__2019.pdf}{Upper-Confidence
	Bound for Channel Selection in LPWA Networks with Retransmissions},
	by \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L. Besson}, J.
	Manco-Vasquez,
  \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{https://sites.google.com/view/wcncworkshop-motion2019/}{MoTION Workshop} at
  \href{http://wcnc2019.ieee-wcnc.org/}{IEEE WCNC},
  Marrakech, Maroc, April 2019, \href{https://hal.inria.fr/hal-02049824}{HAL-02049824}.
\item
  \href{https://perso.crans.org/besson/articles/BBM__IEEE_WCNC_2019.pdf}{GNU
  Radio Implementation of MALIN: « Multi-Armed bandits Learning for
  Internet-of-things Networks »}, by \textbf{L. Besson},
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2019.ieee-wcnc.org/}{IEEE WCNC},
  Marrakech, Maroc, April 2019, \href{https://hal.inria.fr/hal-02006825}{HAL-02006825}.
\item
  \href{https://perso.crans.org/besson/articles/BBM__Demo_ICT_2018.pdf}{MALIN:
  « Multi-Arm bandit Learning for Iot Networks » with GRC: A TestBed
  Implementation and Demonstration that Learning Helps}, by \textbf{L.
  Besson}, \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}. Demonstration
  presented at ICT (\emph{International Conference on Communication}),
  Saint-Malo, France, June 2018. Cf. \texttt{YouTu.be/HospLNQhcMk}, \href{https://hal.inria.fr/hal-02013866}{HAL-02013866}
\item
  \href{https://hal.inria.fr/hal-01629733/document}{Multi-Player Bandits
  Revisited}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}.
  \href{http://www.cs.cornell.edu/conferences/alt2018/accepted.html}{ALT}
  (\emph{Algorithmic Learning Theory}), Lanzarote, Spain, April 2018,
  \href{https://hal.inria.fr/hal-01629733}{HAL-01629733}.
\item
  \href{https://hal.inria.fr/hal-01705292/document}{Aggregation of
  Multi-Armed Bandits learning algorithms for Opportunistic Spectrum
  Access}, by \textbf{L. Besson},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2018.ieee-wcnc.org/}{IEEE WCNC}, Barcelone, Spain,
  avril 2018, \href{https://hal.inria.fr/hal-01705292}{HAL-01705292}.
\item
  \href{https://hal.inria.fr/hal-01575419/document}{Multi-Armed Bandit
  Learning in IoT Networks and non-stationary settings}, by
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L.
  Besson}, \href{https://moychris.wordpress.com/}{C. Moy},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& J. Palicot. \href{http://crowncom.org/2017/}{CrownCom}
  (\emph{Conference on Cognitive Radio Oriented Wireless Networks}),
  Lisbonne, Portugal, September 2017,
  \href{https://hal.inria.fr/hal-01575419}{HAL-01575419}, \textbf{Best Paper Award}.
\end{etaremune}

@@

\section*{Other National Communications}
\renewcommand{\labelenumi}{[ONC-\arabic{enumi}]}
\begin{etaremune}
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{Journ\'{e}e Des Doctorants de l'IETR}, Rennes, France, Jul 2017, \href{https://hal.inria.fr/hal-02013847}{HAL-02013847}
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{SCEE Seminar}, Rennes, France, March 2017
	\item	R. Bonnefoi, \textbf{L. Besson}, ``Multi-Armed Bandit Learning in IoT Networks'', in \emph{Journ\'{e}e Des Doctorants de l'IETR}, Rennes, France, Jun 2016, \href{https://hal.inria.fr/hal-02013839}{HAL-02013839}
\end{etaremune}

\section*{Other Publications}
\renewcommand{\labelenumi}{[OP-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://hal.inria.fr/hal-XXX/document}{Decentralized Spectrum Learning for IoT Wireless Networks Collision Mitigation}, by \href{https://moychris.wordpress.com/}{C. Moy} \& \textbf{L. Besson}, March 2019.
  % \href{https://hal.inria.fr/hal-XXX}{HAL-XXX}.
\item
  \href{https://hal.inria.fr/hal-02006471/document}{Analyse non asymptotique d'un test séquentiel de détection de ruptures et application aux bandits non stationnaires}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}, March 2019,
  \href{https://hal.inria.fr/hal-02006471}{HAL-02006471}.
\item
  \href{https://hal.inria.fr/hal-02006471/document}{The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}, February 2019,
  \href{https://hal.inria.fr/hal-02006471}{HAL-02006471}.
\item
	\href{https://hal.inria.fr/hal-01840022/document}{SMPyBandits: an
	Open-Source Research Framework for Single and Multi-Players Multi-Arms
	Bandits (MAB) Algorithms in Python}, by \textbf{L. Besson},
	active development since 2016,
	\href{https://hal.inria.fr/hal-01840022}{HAL-01840022}. Code on
	\href{https://GitHub.com/SMPyBandits/SMPyBandits}{GitHub.com/SMPyBandits}
	(about 40000 lines), documentation and tutorials on
	\href{https://SMPyBandits.rtfd.io}{SMPyBandits.rtfd.io}.
\item
	\href{https://hal.inria.fr/hal-01736357/document}{What Doubling-Trick
	Can and Can't Do for Multi-Armed Bandits}, by \textbf{L. Besson} \&
	\href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
	Kaufmann}, September 2018,
	\href{https://hal.inria.fr/hal-01736357}{HAL-01736357}.
\item
	\href{https://hal.inria.fr/hal-01847480/document}{A Note on the Ei
	Function and a Useful Sum-Inequality}, by \textbf{L. Besson}, February
	2018 \href{https://hal.inria.fr/hal-01847480}{HAL-01847480}.
\end{etaremune}
